---
title: "covid-app"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading the data and packages

```{r data, message=FALSE,error=FALSE}
library(ggplot2)
library(dplyr)
library(reshape2)
library(forecast)
library(leaflet)
data = read.csv('covid-data.csv')
data[1:10,1:4]
```

# Data manipulations

### Getting dates

```{r world}
data_dates = data[,5:96]
dates = colnames(data_dates)
```
### Adding the map

We take the square root of the numeric data so that the marker for the country with 2 times more cases has 2 times the area.

```{r, message = FALSE, warning=FALSE}
rad = apply(data_dates,2,sqrt)/10
leaflet(data= data) %>% addTiles() %>%
addCircleMarkers(lng = ~Long, lat = ~Lat, weight = 1,radius = ~(rad[,50]), popup= paste("Region:",data$Country.Region,"<br>","Infected", data_dates[,50]))
```

### Getting data for the world
Summing all columns to get aggregated numbers for the world.
```{r}
allCases = colSums(data_dates)
allCases = data.frame(allCases)
ggplot(allCases, aes(x = 1:length(data_dates),y = allCases))+geom_line()+ labs(title = "All cases since 22.01.2020") +  xlab(label = "Days since outbreak") + ylab(label = 'Number of cases')
        
      
```

### Grouping by continent
Using function *summarise_at* we can define the columns in the dataframe we are interested in, to apply *sum* function. In other words - we sum number of cases for each day for each country belonging to the given continent.

```{r}
Continents <- data %>% group_by(Region.Name) %>% summarise_at(dates,sum)
```
### Plot for continents
```{r,echo = FALSE}
continentNames = vector()
for (continent in Continents$Region.Name){
  continentNames = c(continentNames,continent)
}
continentNames[1] = "Other"
numbers =Continents[,2:93]
numbers = t(numbers)
numbers = data.frame(numbers)
colnames(numbers) = continentNames
rownames(numbers) = 1:92
days = 1:92
Continents_graph = data.frame(days,numbers)
continents.melted <- melt(Continents_graph, id = "days")
ggplot(data = continents.melted, aes(x = days, y = value, color = variable)) +
 geom_line() + xlab(label = "Days since 22.01.2020") + ylab(label = 'Number of cases')

```

### Grouping by country
Similar to grouping by continent. 
```{r}
Countries <- data %>% group_by(Country.Region) %>% summarise_at(dates,sum)
Countries[1:5,1:4]
```
# Data analysis
### Adding forecasts
We feed the past data to the *forecast* function to obtain simple prediction.
```{r, echo = FALSE}
countryNames = vector()
for (country in Countries$Country.Region){
  country = gsub("[^(a-zA-Z)|//)]", "", country)
  country = gsub("\\)|\\(", "", country)
  countryNames = c(countryNames,country)
  
}
numbers =Countries[,2:93]
numbers = t(numbers)
numbers = data.frame(numbers)
colnames(numbers) = countryNames
rownames(numbers) = 1:92
days = 1:92
Countries_graph = data.frame(days,numbers)
```



```{r}
fcast = forecast(Countries_graph[,'China'])
plot(fcast, main = c('China', "forecast"), ylab = "Number of cases", xlab= 'Days since outbrake 22.01.2020')
```


